A protocol \& event-sourced database for decentralized user-siloed data

### 2021-03-31 whitepaper/old_draft.tex
feat: updates to use new pandoc and features
Signed-off-by: Carson Farmer <carson.farmer@gmail.com>

For most apps, it is critical to have reliable mechanisms for publishing updates and events (i.e., to support event-driven architectures), scalability (optimized write and read operations), forward-compatible application updates (e.g., code changes, retroactive events), auditing systems, etc. To support such requirements, developers have begun to utilize event sourcing and command query responsibility segregation (CQRS) patterns \cite{bettsExploringCQRSEvent2013}, relying on append-only logs to support immutable state histories. Indeed, a number of commercial and open source software projects have emerged in recent years that facilitate ES and CQRS-based designs, including Event Store \cite{EventStore}, Apache Kafaka \cite{ApacheKafka} and Samza \cite{ApacheSamza}, among others \cite{kleppmannDesigningDataintensiveApplications2017}.

>>>>

For most apps, it is critical to have reliable mechanisms for publishing updates and events (i.e., to support event-driven architectures), scalability (optimized write and read operations), forward-compatible application updates (e.g., code changes, retroactive events), auditing systems, etc. To support such requirements, developers have begun to utilize event sourcing and command query responsibility segregation (CQRS) patterns \cite{bettsExploringCQRSEvent2013}, relying on append-only logs to support immutable state histories. Indeed, a number of commercial and open source software projects have emerged in recent years that facilitate ES and CQRS-based designs, including Event Store \cite{EventStore}, Apache Kafka \cite{ApacheKafka} and Samza \cite{ApacheSamza}, among others \cite{kleppmannDesigningDataintensiveApplications2017}.
